---
title: "CovidHunShinyPred"
author: "holliPista"
date: '2021 03 16 '
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyr)
library(gsheet)
```

## Overview

There are no more current topic than the Covid-19. As the 'Shiny Application and 
Reproducible Pitch' I've made a quick visualization of the Hungarian fatality 
and share of positive tests. It's the seed of a prediction project but just the
first explanatory step, hence please do not expect any fancy thing.

You can find the project on the following github link: 
<https://github.com/hollipista/CovidHunShinyPred>

Further information about the data: <https://atlo.team/koronamonitor/>

And here is the shiny app: <https://hollipista.shinyapps.io/CovidHunShinyPred/>

## Dataframe

I have a subsection of original dataset for further predictions, you can see below:

```{r echo = FALSE, warning=FALSE}
covidhu<-gsheet2tbl('https://docs.google.com/spreadsheets/d/1e4VEZL1xvsALoOIq9V2SQuICeQrT5MtWfBm32ad7i8Q')
covidhu<-covidhu[,c(1,3,12,17,18,19,20,21,33)]
names(covidhu)[1] <- "Date"
names(covidhu)[2] <- "NewCases"
names(covidhu)[3] <- "ActiveInfected"
names(covidhu)[4] <- "PositiveTestSHR"
names(covidhu)[5] <- "Fatality"
names(covidhu)[6] <- "Recovered"
names(covidhu)[7] <- "Hospitalized"
names(covidhu)[8] <- "VentilatorTreated"
names(covidhu)[9] <- "Vaccinated"
```

```{r echo = TRUE}
head(covidhu)
```


## Original mortality figures

As you can see there's quite huge fluctuation in the figures. We have to handle
the variability of the variables. It has a noisy nature of course but the 
uneven data provision is also an important factor. 

```{r echo = TRUE}
plot(covidhu$Fatality,type='l')
```

## "Manual" for the shiny app

I've chosen the share of positive test variable for this project. You can see
a linechart made by ggplot, with the absolute number of daily fatal cases and 
the mentioned positive test share data. 

You can apply different moving averages stepped by days (default is 0 that means
no applied moving average), and also shift the tests with lag function as the
identified amount of diseased results in lethal results with a certain delay - 
of course.

Please do not take my project seriously, it's about a tiny play around shiny.

And again, here is a the app: <https://hollipista.shinyapps.io/CovidHunShinyPred/>



Thanks for you grading!

